\texttt{SuperScreen}: An open-source package for simulating the magnetic response of 2D superconductors

### 2021-08-02 main_cpc.tex
Updates from Overleaf

Each layer can contain one or more superconducting films which may have one or more holes in them. Films and holes are represented by instances of the \mintinline{python}{superscreen.Polygon} class. A \mintinline{python}{Polygon} contains the name of the layer to which is belongs, an array specifying the coordinates of its vertices, and a method, \mintinline{python}{Polygon.contains_points()}, which determines whether specified coordinates lie within the polygon or not. In addition to superconducting films and holes, one may define ``abstract regions,'' which are polygons that need not correspond to a physical feature in the structure, but will still be meshed. Abstract regions can be used to define a ``bounding box" around a structure. The \mintinline{python}{superscreen.geometry} module provides functions for generating the underlying polygon vertices for simple geometries (circles and rectangles). See Code Block~\ref{code:device} for an example of a function that creates a square or circular superconducting ring centered at the origin.

\begin{code}
\begin{minted}[fontsize=\footnotesize]{python}
import superscreen as sc

def make_ring(
    inner_radius=2.5,
    outer_radius=5,
    Lambda=1,
    length_units="um",
    square=False,
):
    if square:
        name = "square_ring"
        outer_points = sc.geometry.square(
            outer_radius * 2, points_per_side=60
        )
        inner_points = sc.geometry.square(
            inner_radius * 2, points_per_side=20
        )
        bbox_points = sc.geometry.square(
            outer_radius * 2 * 1.4, points_per_side=5
        )
    else:
        name = "circular_ring"
        outer_points = sc.geometry.circle(outer_radius)
        inner_points = sc.geometry.circle(inner_radius)
        bbox_points = sc.geometry.circle(outer_radius * 1.4, points=21)

    layers = [sc.Layer("base", Lambda=Lambda, z0=0)]
    films = [sc.Polygon("ring", layer="base", points=outer_points)]
    holes = [sc.Polygon("hole", layer="base", points=inner_points)]
    abstract_regions = [
        sc.Polygon("bounding_box", layer="base", points=bbox_points),
    ]
    return sc.Device(
        name,
        layers=layers,
        films=films,
        holes=holes,
        abstract_regions=abstract_regions,
        length_units=length_units,
    )
\end{minted}
\captionof{listing}{A function that creates a \mintinline{python}{Device} representing a circular or square ring centered at the origin.}
\label{code:device}
\end{code}

@@

\begin{figure}
\centering
\begin{subfigure}{.4\textwidth}
  \centering
  \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_uniform_plot_currents.png}
  \caption{Circular ring sheet current.}
  \label{fig:circular_ring_plot_currents}
\end{subfigure}
\begin{subfigure}{.4\textwidth}
  \centering
  \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_uniform_plot_fields.png}
  \caption{Circular ring magnetic field.}
  \label{fig:circular_ring_plot_fields}
\end{subfigure}

\begin{subfigure}{.4\textwidth}
  \centering
  \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_circ_plot_currents.png}
  \caption{Square ring sheet current.}
  \label{fig:square_ring_plot_currents}
\end{subfigure}
\begin{subfigure}{.4\textwidth}
  \centering
  \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_circ_plot_fields.png}
  \caption{Square ring magnetic field.}
  \label{fig:square_ring_plot_fields}
\end{subfigure}

\caption{Sheet current $\vec{J}$ and magnetic field $\mu_0H_z$ distributions for the circular (top) and square (bottom) ring calculated using Code Block~\ref{code:ring_circulating_current}.}
\label{fig:ring_plot_fields_currents}
\end{figure}

The output of \mintinline{python}{superscreen.solve()} is a \mintinline{python}{list} of \mintinline{python}{superscreen.Solution} objects, with a length of 1 plus the number of iterations used for the iterative portion of the calculation. A \mintinline{python}{Solution} encapsulates all of the information about a solved model: the \mintinline{python}{Device}, applied field, circulating currents, and calculated stream functions and magnetic fields for all layers in the device. A \mintinline{python}{Solution} also has methods for processing the simulation results, including:
\begin{itemize}
    \item{
    \mintinline{python}{Solution.grid_data()}: Interpolates the calculated stream functions and magnetic fields for each layer from the triangular mesh to a rectangular grid.
    }
    \item{
    \mintinline{python}{Solution.current_density()}: Interpolates the stream functions to a rectangular grid and calculates the current density (sheet current) $\vec{J}(x, y)$ in each layer using Eq.~\ref{eq:stream}.
    }
    \item{
    \mintinline{python}{Solution.polygon_flux()}: Calculates the total flux through each polygon in the device (films, holes, and abstract regions).
    }
    \item{
    \mintinline{python}{Solution.field_at_position()}: Calculates the vector magnetic field at any point(s) in space due the applied field and the currents flowing the in the device using Eqs.~\ref{eq:field_from_kernel} and \ref{eq:kernels}.
    }
\end{itemize}

>>>>

Each layer can contain one or more superconducting films which may have one or more holes in them. Films and holes are represented by instances of the \mintinline{python}{superscreen.Polygon} class. A \mintinline{python}{Polygon} contains the name of the layer to which is belongs, an array specifying the coordinates of its vertices, and a method, \mintinline{python}{Polygon.contains_points()}, which determines whether specified coordinates lie within the polygon or not. In addition to superconducting films and holes, one may define ``abstract regions,'' which are polygons that need not correspond to a physical feature in the structure, but will still be meshed. Abstract regions can be used to define a ``bounding box" around a structure. The \mintinline{python}{superscreen.geometry} module provides functions for generating the underlying polygon vertices for simple geometries (circles and rectangles). See Code Block~\ref{code:device} for an example of a function that creates a square or circular superconducting ring centered at the origin, with an effective penetration depth $\Lambda = 1\,\mu\mathrm{m}$.

\begin{code}
\begin{minted}[fontsize=\footnotesize]{python}
import superscreen as sc
import superscreen.geometry as geo

def make_ring(
    inner_radius=2.5,
    outer_radius=5,
    Lambda=1,
    length_units="um",
    square=False,
):
    if square:
        name = "square_ring"
        outer = geo.square(outer_radius * 2, points_per_side=60)
        inner = geo.square(inner_radius * 2, points_per_side=20)
        bbox = geo.square(outer_radius * 2 * 1.4, points_per_side=5)
    else:
        name = "circular_ring"
        outer_points = geo.circle(outer_radius)
        inner_points = geo.circle(inner_radius)
        bbox = geo.circle(outer_radius * 1.4, points=21)

    layers = [sc.Layer("base", Lambda=Lambda, z0=0)]
    films = [sc.Polygon("ring", layer="base", points=outer_points)]
    holes = [sc.Polygon("hole", layer="base", points=inner_points)]
    abstract_regions = [
        sc.Polygon("bounding_box", layer="base", points=bbox),
    ]
    return sc.Device(
        name,
        layers=layers,
        films=films,
        holes=holes,
        abstract_regions=abstract_regions,
        length_units=length_units,
    )
\end{minted}
\captionof{listing}{A function that creates a \mintinline{python}{Device} representing a circular or square ring centered at the origin.}
\label{code:device}
\end{code}

@@

\begin{figure}
\centering
\begin{subfigure}{.4\textwidth}
  \centering
  \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_uniform_plot_currents.png}
  \caption{Screening current, uniform applied field model.}
  \label{fig:circular_ring_plot_currents}
\end{subfigure}
\begin{subfigure}{.4\textwidth}
  \centering
  \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_uniform_plot_fields.png}
  \caption{Total magnetic field, uniform applied field model.}
  \label{fig:circular_ring_plot_fields}
\end{subfigure}

\begin{subfigure}{.4\textwidth}
  \centering
  \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_circ_plot_currents.png}
  \caption{Screening current, trapped flux model.}
  \label{fig:square_ring_plot_currents}
\end{subfigure}
\begin{subfigure}{.4\textwidth}
  \centering
  \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_circ_plot_fields.png}
  \caption{Total magnetic field, trapped flux model.}
  \label{fig:square_ring_plot_fields}
\end{subfigure}

\caption{Sheet current $\vec{J}$ and magnetic field $\mu_0H_z$ distributions for the circular ring with a uniform applied field of 0.25 mT (top) and a circulating current of 1 mA (bottom) calculated using Code Block~\ref{code:ring_circulating_current}.}
\label{fig:ring_plot_fields_currents}
\end{figure}

The output of \mintinline{python}{superscreen.solve()} is a \mintinline{python}{list} of \mintinline{python}{superscreen.Solution} objects, with a length of 1 plus the number of iterations used for the iterative portion of the calculation. A \mintinline{python}{Solution} encapsulates all of the information about a solved model: the \mintinline{python}{Device}, applied field, circulating currents, and calculated stream functions and magnetic fields for all layers in the device. A \mintinline{python}{Solution} also has methods for processing the simulation results, including:
\begin{itemize}
    \item{
    \mintinline{python}{Solution.grid_data()}: Interpolates the calculated stream functions and magnetic fields for each layer from the triangular mesh to a rectangular grid.
    }
    \item{
    \mintinline{python}{Solution.current_density()}: Interpolates the stream functions to a rectangular grid and calculates the current density (sheet current) $\vec{J}(x, y)$ in each layer using Eq.~\ref{eq:stream}.
    }
    \item{
    \mintinline{python}{Solution.polygon_flux()}: Calculates the total flux through each polygon in the device (films, holes, and abstract regions).
    }
    \item{
    \mintinline{python}{Solution.field_at_position()}: Calculates the vector magnetic field at any point(s) in space due the applied field and the currents flowing the in the device using Eqs.~\ref{eq:field_from_kernel} and \ref{eq:kernels}.
    }
\end{itemize}
\mintinline{python}{Solutions} also have several visualization methods built in (see Section~\ref{section:overview:visualization}).
